Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-12-15 docs/manuscript/manuscript.tex
Update survey response demographics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures and materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF). 
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
We amended that plan at the close of data collection to reflect a change in stopping rule we used to end the survey.

@@

@@

\subsection*{Survey Demographics}
A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}

\begin{itemize}
    \item Include a text summary of the key in sample characteristics summarized in Table 1a and 1b.
\end{itemize}

\subsection*{Aggregate Measures Along 4-Dimensions}
This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).

@@

\subsubsection*{Familiarity with Reproduciblity Practices}

\subsubsection*{Frequency of Reproduciblity Practices}

Q9 will feather in to contextualize the measure

\subsubsection*{Barriers to Reproduction}
Discussion of details from Q14

\subsection{Actual Reproductions}
Start with the outline of what the population is here because not all respondents answered these questions. Start with descriptives that show this sub-sample of respondents. Summary discussion of Q10-Q12.

\subsection*{Definition of Reproducibility}
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusion}
A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures and materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials and along with a complete history of their development. 
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
We later amended that plan to reflect a change in stopping rule we used to end the survey and to include additional statistical analyses we conducted after viewing the survey response.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Survey Response Demographics}
A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly well balanced across the disciplinary subfields - Human Geography (30.7\%), Physical Geography (29.8\%), Nature and Society (10.1\%), Geographic Methods and GISci (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Aggregate Measures Along 4-Dimensions}
This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).

@@

%%%%%%%%%%%
\subsubsection*{Definition of Reproducibility}
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

%%%%%%%%%%%
\subsubsection*{Familiarity with Reproduciblity Practices}

%%%%%%%%%%%
\subsubsection*{Frequency of Reproduciblity Practices}
Q9 will feather in to contextualize the measure

%%%%%%%%%%%
\subsubsection*{Barriers to Reproduction}
Discussion of details from Q14

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Actual Reproductions}
Start with the outline of what the population is here because not all respondents answered these questions. Start with descriptives that show this sub-sample of respondents. Summary discussion of Q10-Q12.

@@

\begin{itemize}
    \item The reproducibility literature emphasizes quantitative, particularly computational, forms of research. This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography). These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies. This fact suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.
    \item A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusion}
